`r glue::glue('Doublet benchmarking results: {params$dataset}')`

### 2024-07-23 analyses/doublet-detection/template-notebooks/02_explore-benchmark-results.Rmd

@@

```{r fig.width = 8}

@@

```{r fig.width = 8}
d_plot <- plot_pca(
  doublet_df, 
  color_column = scrublet_prediction,
  color_lab = "scrublet prediction"
)

@@

```{r}
# just need a single score pca for this case
# we'll provide the least stringent predictions; this only affects point layering in the plot
plot_pca(
  doublet_df, 
  color_column = cxds_score, 
  pred_column = cxds_prediction_0.5,
  color_type = "c",
  color_lab = glue::glue("cxds scores")
)
```

>>>>

```{r}
# Check if scores are present, to determine if certain chunks should be run
has_scdbl <- !all(is.na(doublet_df$scdbl_score))
has_cxds <- !all(is.na(doublet_df$cxds_score))
has_scrublet <- !all(is.na(doublet_df$scrublet_score))
```

@@

```{r, eval = has_scdbl, fig.width = 8}

@@

```{r, eval = has_scrublet, fig.width = 8}
d_plot <- plot_pca(
  doublet_df,
  color_column = scrublet_prediction,
  color_lab = "scrublet prediction"
)

@@

```{r, eval = has_cxds}
# just need a single score pca for this case
# we'll provide the least stringent predictions; this only affects point layering in the plot
plot_pca(
  doublet_df,
  color_column = cxds_score,
  pred_column = cxds_prediction_0.5,
  color_type = "c",
  color_lab = glue::glue("cxds scores")
)
```
